\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    % \textbf{#1}{: #2 \vspace{-2pt}}
    #1
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/yuvarajravichandran}{\Large Yuvaraj Ravichandran}} & Email : \href{mailto:\email}{\email}\\
  \href{https://www.linkedin.com/in/yuvarajravichandran}{www.linkedin.com/in/yuvarajravichandran} & Mobile : \href{tel:\mobile}{\mobile} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sona College of Technology}{Salem, Tamilnadu, India}      
      {Bachelor of Engineering in Electrical and Electronics;  CGPA: 8.77/10}{2007 -- 2011}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Barclays Global Service Centre Pvt. Ltd.}{Chennai, Tamilnadu, India}
      {AVP}{Feb. 2020 ‑ Present}
      \resumeItemListStart
        \resumeItem
          {Developed high performance in house reconciliation product from scratch in a fast paced environment. I have handled design and architecture of core components including in-memory matching engine, ETL layer to name a few. Due to low latency, we were able to reduce the runtime of existing high volume reconciliations, which were running on market leading legacy systems, from hours to mins. This helps the bank greatly to find and mitigate risks faster. And this is considered as a strategic tool to replace existing licensed ones across the bank}
        \resumeItem
          {Managed a team of 8 engineers including vendors with focus on high quality deliveries on time. I have involved in task assignments, design discussion and mentoring them on implementation specifics}
        \resumeItem
          {Volunteered on tech debt mitigation program which was aimed to migrate legacy systems to latest version of Java and completed them successfully. This was considered as one of the great achievement due to low to no knowledge about those systems existed in our team}
        \resumeItem
          {I have involved in Flash EOL mitigation for few of our legacy systems, where we successfully migrated the frontend to Angular along with their services to Spring based REST APIs within short span of time}
        \resumeItem
          {Designed and developed in house break management system to manage results of our reconciliations. This involves various sub-components like proofing, carry over, duplicate check, reporting, static data management etc. I have involved in designing database layer for day 1 architecture}
        \resumeItem
          {I have been part of implementing git workflow, CI/CD pipelines, and setting up internal artifact repository}
        
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Citicorp Services India Pvt. Ltd.}{Chennai, Tamilnadu, India}
      {Application Developer Intermediate Programmer Analyst}{Oct. 2016 ‑ Feb. 2020}
      \resumeItemListStart
        \resumeItem
          {Developed real‑time reconciliation data processing system using Lambda architecture to crunch billions of records}
        \resumeItem
          {Redesigned matching layer to achieve 12k messages/sec with sub milli second latency using space based architecture using distributed data grid like Hazelcast}
        \resumeItem
          {Migrated the transformation layer from batch to streaming platform (Storm/Kafka) to provide 6X performance}
        \resumeItem
          {I have been part of design and development of real‑time break management system using Elastic stack to reduce report timing from minutes to seconds}
        \resumeItem
          {Designed and Implemented the initial version of CI/CD pipeline using TeamCity and Urbancode Deploy}
        \resumeItem
          {I have been part of setting up infrastructure for Kafka, Storm and ELK clusters on bare metal VMs}
      \resumeItemListEnd

    \resumeSubheading
      {Infrasoft Technologies Ltd. (Client ‑ BNP Paribas Securities Ltd.)}{Chennai, Tamilnadu, India}
      {Senior Associate Consultant}{Sep. 2015 ‑ Oct. 2016}
      \resumeItemListStart
        \resumeItem
          {Implemented multiple new features to collect and process SWIFT messages from multiple sources every day}
        \resumeItem
          {Helped the team to identify and fix critical bugs in Corporate action straight through processes}
      \resumeItemListEnd

    \resumeSubheading
      {BNY Mellon Technology Pvt. Ltd. (Inautix)}{Chennai, Tamilnadu, India}
      {Senior Application Developer}{Aug. 2011 ‑ Sep. 2015}
      \resumeItemListStart
        \resumeItem
          {Developed template configuration management system to ease the initial account setup process}
        \resumeItem
          {Lead the integration of Advisor model management system with New account opening using RESTful webservices}
        \resumeItem
          {Fixed some of the performance bottlenecks with the help of Dynatrace reports}
        \resumeItem
          {I have been part of many production deployment and L3 support for New account opening system}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%     \resumeSubItem{Github Visualization}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{Recommendation System}
%       {Music and Movie recommender systems using collaborative filtering on public datasets.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%   \resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Java, Javascript, SQL}
   }
   \item{
    \textbf{Technologies}{: MSSQL, Oracle, Spring, Apache Storm, Apache Cassandra, Apache Kafka, Elastic Stack (ELK), RocksDB, TeamCity, IBM UrbanCode Deploy}
  }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}